---
title: "LHA_scRNAseq_integration_2020"
output: html_notebook

Seurat version: 3.1.3
chunk_output_type: inline

---
```{r}
library(Seurat)
```
 

#Load three LHA datasets (Seurat Objects)
```{r}
load('/Users/wangy6/Desktop/DATA/LHA_scRNAseq/2020_reanalysis/lha_sternson_2020Nov.Robj')
load('/Users/wangy6/Desktop/DATA/LHA_scRNAseq/2020_reanalysis/lha_jackson_neuron_2020Nov.Robj')
load('/Users/wangy6/Desktop/DATA/LHA_scRNAseq/2020_reanalysis/lha_stuber_neuron_2020Nov.Robj')
```


```{r}
total.genes <- list(rownames(LHA_Jackson_combined_neurons@assays$RNA),rownames(LHA_Stuber_combined_neuron@assays$RNA),rownames(LHA_Trace@assays$RNA))
common.genes <- Reduce(f = intersect, x = total.genes)
```

```{r}
LHA_Jackson_combined_neurons<- subset(LHA_Jackson_combined_neurons,features=common.genes)
LHA_Stuber_combined_neuron<- subset(LHA_Stuber_combined_neuron,features=common.genes)
LHA_Trace<- subset(LHA_Trace,features=common.genes)
```
# Filter out cells with low quality and doublets or multiplets from the datasets
```{r}
LHA_Stuber_combined_neuron <- subset(LHA_Stuber_combined_neuron, subset = nFeature_RNA > 500 & nFeature_RNA < 7500 & nCount_RNA < 2e+05)
LHA_Jackson_combined_neurons<- subset(LHA_Jackson_combined_neurons, subset = nFeature_RNA > 500 & nFeature_RNA < 7500 & nCount_RNA < 2e+05)
LHA_Trace<- subset(LHA_Trace, subset = nFeature_RNA > 500 & nFeature_RNA < 7500 & nCount_RNA < 2e+05)
```

```{r}
LHA.list=c(LHA_Jackson_combined_neurons,LHA_Trace,LHA_Stuber_combined_neuron)
```

# Identify variable features and perform data integration
```{r}
for (i in 1:length(LHA.list)) {
    LHA.list[[i]] <- FindVariableFeatures(LHA.list[[i]], selection.method = "vst", 
        nfeatures = 2000, verbose = TRUE)
}
lha.anchors <- FindIntegrationAnchors(object.list = LHA.list, dims = 1:30)
lha.integrated <- IntegrateData(anchorset = lha.anchors , dims = 1:30,features.to.integrate = common.genes)
```
# Modify metadata so that they would make sense ("SeuratProject" -> LHA_10x; "Q5","Q6","Q7","Q8" -> LHA_SCRB)
```{r}
lha.integrated_neurons=lha.integrated # just to change the object name to avoid confusion
Idents(lha.integrated_neurons)='orig.ident'
lha.integrated_neurons <- RenameIdents(object = lha.integrated_neurons, 'SeuratProject' = 'LHA_10x','Q5' = 'LHA_SCRB','Q6' = 'LHA_SCRB','Q7' = 'LHA_SCRB','Q8' = 'LHA_SCRB')

lha.integrated_neurons <- AddMetaData(
    object = lha.integrated_neurons,
    metadata =Idents(lha.integrated_neurons),
    col.name = 'scRNAseq_sources')
```

# switch to integrated assay. The variable features of this assay are automatically
# set during IntegrateData
```{r}
DefaultAssay(lha.integrated_neurons) <- "integrated"
#DefaultAssay(lha.integrated_neurons) <- "RNA"
```
# Scale data and run PCA
```{r}
lha.integrated_neurons=ScaleData(lha.integrated_neurons)
lha.integrated_neurons <- RunPCA(lha.integrated_neurons, verbose = FALSE)
lha.integrated_neurons <- RunUMAP(lha.integrated_neurons, dims = 1:30)
lha.integrated_neurons <- RunTSNE(lha.integrated_neurons, seed.use=3,dims = 1:30,perplexity=40)
```
# Evaluate the performance of PCA
```{r}
lha.integrated_neurons <- JackStraw(lha.integrated_neurons, num.replicate = 100)
lha.integrated_neurons <- ScoreJackStraw(lha.integrated_neurons, dims = 1:20)
JackStrawPlot(lha.integrated_neurons, dims = 1:15)
ElbowPlot(lha.integrated_neurons)
```
# Clustering analysis (initial analysis, this is before optimization)
```{r}
lha.integrated_neurons <- FindNeighbors(lha.integrated_neurons, dims=1:30)
lha.integrated_neurons <- FindClusters(lha.integrated_neurons, resolution = 0.5)
```
# Visualizations
```{r,fig.height=5, fig.width=15, message=FALSE, warnings=FALSE}
DimPlot(lha.integrated_neurons, reduction = "tsne", group.by = "scRNAseq_sources",,split.by = "scRNAseq_sources",pt.size=1)+FontSize(x.text = 26,y.text = 26,x.title = 28, y.title = 28, main=500) + BoldTitle() +NoLegend()
```

```{r}
DimPlot(lha.integrated_neurons, reduction = "umap",   group.by = "ident", label=TRUE)
```

```{r}
DimPlot(lha.integrated_neurons, reduction = "tsne",  group.by = "ident", label=TRUE)
```

##   Save data
```{r}
#Save the Seurat object for further analysis in part 2
save(lha.integrated_neurons,file="/Users/wangy6/Desktop/DATA/LHA_scRNAseq/2020_reanalysis/lha_integrated_neurons_2020Nov.Robj")
```
